Robots, Are They Overlords or Serf-Laborers?

### 2015-06-13 draft1.tex
Add .gitignore file

% plagiarism check
% cohesion check
% grammar check (firt two page of new paper)
\documentclass[man]{apa6}
\title{Robots, Are They Overlords or Serf-Laborers?}
\author{Murat Ambarkutuk}
\affiliation{English Language Institute, University of Delaware \\ murata@udel.
edu}
\note{First Draft; 6/8/2015; \LaTeX}
\usepackage{apacite}
% modify it!
\abstract{Of all the tools and methods invented by humankind to tame nature and make use of its challenges, the invention of computer has had the greatest impact on society.
 Coupled with the Internet, computers have changed the way billions of humans work, entertain themselves, and think.
 Since the rise of the computers, Artificial Intelligence (AI) has been one of the most debated issues in the field of engineering.
 Research toward robotics is also based upon the creation of AI that will run the robots thanks to superior cognitive and perceptive abilities of AI than that of man. 
 However, many researchers argue that the creation of AI will deeply elevate society and it will help humankind to solve major societal problems, while others refute the arguments for that conceptual invention because of ethical problems that AI will bring.
 This paper explores the ethical problems that the creation of AI will raise, and it attributes these problems to widely varying definitions and the applications of these technologies.
}
\keywords{artificial intelligence, robotics, ethics, society} 
\shorttitle{Overlords vs. Serf-Laborers}
\leftheader{Even-Numbered Page Header} %Change it
\begin{document}
\maketitle

>>>>

% plagiarism check
% cohesion check
% grammar check (firt two page of new paper)
\documentclass[man]{apa6}
\title{Robots, Are They Overlords or Serf-Laborers?}
\author{Murat Ambarkutuk}
\affiliation{English Language Institute, University of Delaware \\ murata@udel.
edu}
\note{First Draft; 6/8/2015; \LaTeX}
\usepackage{apacite}
% modify it!
\abstract{Of all the tools and methods invented by humankind to tame nature and make use of its challenges, the invention of computer has had the greatest impact on society.
 Coupled with the Internet, computers have changed the way billions of humans work, entertain themselves, and think.
 Since the rise of the computers, Artificial Intelligence (AI) has been one of the most debated issues in the field of engineering.
 Robots are also subject to these debates because that tangible spin-off technology that will be run by such an AI that will have superior cognitive and perceptive abilities than that of man. 
 However, many researchers argue that the creation of AI will deeply elevate society and it will help humankind to solve major societal problems, while others refute the arguments for that conceptual invention because of ethical problems that AI will bring.
 This paper explores the ethical problems that the creation of AI will raise, and it attributes these problems to widely varying definitions and the applications of these technologies.
}
\keywords{artificial intelligence, robotics, ethics, society} 
\shorttitle{Overlords vs. Serf-Laborers}
\leftheader{Even-Numbered Page Header} %Change it
\begin{document}
\maketitle
